---
title: "Review of relevant variables"
output:
  html_document:
    css: ~/GitHub/brown-2017-disseration/libs/css/sidebar.css
    keep_md: yes
    toc: yes
  word_document:
    toc: yes
date: 'Date: `r Sys.Date()`'
---

<!-- These two chunks should be added in the beginning of every .Rmd that you want to source an .R script -->
<!--  The 1st mandatory chunck  -->
<!--  Set the working directory to the repository's base directory -->
```{r, echo=F, message=F} 
#Don't combine this call with any other chunk 
# cat("Working directory: ", getwd()) # check where you are
  library(knitr)
# Rmd is in "./reports/reportA/reportA.Rmd", but now the root is "./"
  knitr::opts_knit$set(root.dir='../../') 
```


<!--  The 2nd mandatory chunck  -->
<!-- Set the report-wide options, and point to the external code file. -->
```{r set_options, echo=F}
# set options shared by all chunks
opts_chunk$set(
  results='show', 
  message = TRUE,
  comment = NA, 
  tidy = FALSE,
  fig.height = 5, 
  fig.width = 7, 
  out.width = "750px", #550px
  fig.path = 'figure_rmd/',     
  dev = "png",
  dpi = 800
  # fig.path = 'figure_pdf/',     
  # dev = "pdf"#,
  # dev.args=list(pdf = list(colormodel = 'cmyk'))
)
echoChunks <- TRUE
options(width=120 ) #So the output is 50% wider than the default.
# connect to the file with the underlying R script  
read_chunk("./sandbox/eda-1/eda-1.R") 
```



<!-- Load 'sourced' R files.  Suppress the output when loading packages. --> 
```{r load-packages, echo=echoChunks, message=FALSE}
```


<!-- Load the sources.  Suppress the output when loading sources. --> 
```{r load-sources, echo=echoChunks, message=FALSE}
```

# Exposition
<!-- Load any Global functions and variables declared in the R file.  Suppress the output. --> 
```{r declare-globals, echo=echoChunks, results='show', message=FALSE}
```

<!-- Declare any global functions specific to a Rmd output.  Suppress the output. --> 
```{r, echo=echoChunks, message=FALSE}
#Put code in here.  It doesn't call a chunk in the codebehind file.
```

```{r object-glossary, echo=echoChunks, results='show', message=FALSE}
```
## Data
<!-- Load the datasets.   -->
```{r load-data, echo=echoChunks, results='show', message=FALSE}
```

<!-- Inspect the datasets.   -->
```{r inspect-data, echo=echoChunks, results='show', message=FALSE}
```

<!-- Tweak the datasets.   -->
```{r tweak-data, echo=echoChunks, results='show', message=FALSE}
```



<!-- Basic table view.   -->
```{r basic-table, echo=TRUE, results='show', message=FALSE}
```

<!-- Basic graph view.   -->
```{r basic-graph, echo=TRUE, results='show', message=FALSE}
```


```{r eda-a-1, echo=TRUE, results='show', message=FALSE}
```

# Development
This section will contain a close up examination of relevant variables, one by one.

## Static
This section focuses on variables with values that do not change with time.

### id
```{r id, echo=TRUE, results='show', message=FALSE}
```

### male
```{r male, echo=TRUE, results='show', message=FALSE}
```

### race
```{r race, echo=TRUE, results='show', message=FALSE}
```

## Dynamic

### Word List Recall 
```{r word-list-recall, echo=TRUE, results='show', message=FALSE}
```

### Social Support
```{r social-support, echo=TRUE, results='show', message=FALSE}
```

### Loneliness Three Item Short
```{r loneliness-three, echo=TRUE, results='show', message=FALSE}
```

### Loneliness Full Scale
```{r loneliness-eleven, echo=TRUE, results='show', message=FALSE}
```

### Social Network 
```{r socialnetwork_total, echo=TRUE, results='show', message=FALSE}
```

### Close Social Network
```{r close_social_network, echo=TRUE, results='show', message=FALSE}
```

### Activity
```{r close_social_network, echo=TRUE, results='show', message=FALSE}
```

### srmemory
```{r srmemory, echo=TRUE, results='show', message=FALSE}
```

# Recapitulation