---
title: "Results"
output:
  html_document:
    theme: simplex
    toc: true
    toc_depth: 3
    keep_md: true
    toc_float: true
  word_document:
    toc: yes
date: 'Date: `r Sys.Date()`'
---
<!-- These two chunks should be added in the beginning of every .Rmd that you want to source an .R script -->
<!--  The 1st mandatory chunck  -->
<!--  Set the working directory to the repository's base directory -->
```{r, echo=F, message=F} 
#Don't combine this call with any other chunk 
# cat("Working directory: ", getwd()) # check where you are
  library(knitr)
# Rmd is in "./reports/reportA/reportA.Rmd", but now the root is "./"
  knitr::opts_knit$set(root.dir='../../') 
```


<!--  The 2nd mandatory chunck  -->
<!-- Set the report-wide options, and point to the external code file. -->
```{r set_options, echo=F}
# set options shared by all chunks
opts_chunk$set(
  results='show', 
  message = TRUE,
  comment = NA, 
  tidy = FALSE,
  fig.height = 5, 
  fig.width = 7, 
  out.width = "750px", #550px
  fig.path = 'figure_rmd/',     
  dev = "png",
  dpi = 800
  # fig.path = 'figure_pdf/',     
  # dev = "pdf"#,
  # dev.args=list(pdf = list(colormodel = 'cmyk'))
)
echoChunks <- FALSE
options(width=120 ) #So the output is 50% wider than the default.
# connect to the file with the underlying R script  
read_chunk("./sandbox/results-section/model-results.R") 
```

<!-- Load 'sourced' R files.  Suppress the output when loading packages. --> 
```{r load-packages, echo=echoChunks, message=FALSE}
```


<!-- Load the sources.  Suppress the output when loading sources. --> 
```{r load-sources, echo=echoChunks, message=FALSE}
```

# Immediate Word Recall
## Immediate Word Recall Model Fit Indices
```{r immediate-word-recall-model-summaries, echo=echoChunks, message=FALSE}
```

## Immediate Word Recall LCM Parameters
```{r immediate-word-recall-lgm, echo=echoChunks, message=FALSE}
```

## Immediate Word Recall Unconditional ATL Model
```{r immediate-word-recall-atl, echo=echoChunks, message=FALSE}
```


# Delayed Word Recall
## Delayed Word Recall Model Fit Indices
```{r delayed-word-recall-model-summaries, echo=echoChunks, message=FALSE}
```

## Delayed Word Recall LCM Parameters
```{r delayed-word-recall-lgm, echo=echoChunks, message=FALSE}
```

## Delayed Word Recall Unconditional ATL Model
```{r delayed-word-recall-atl, echo=echoChunks, message=FALSE}
```

# Mental Status
## Mental Status Model Fit Indices
```{r mental-status-model-summaries, echo=echoChunks, message=FALSE}
```

## Mental Status LCM Parameters
```{r mental-status-lgm, echo=echoChunks, message=FALSE}
```

## Mental Status Unconditional ATL Model
```{r mental-status-atl, echo=echoChunks, message=FALSE}
```

# Loneliness
## Loneliness Model Fit Indices
```{r loneliness-model-summaries, echo=echoChunks, message=FALSE}
```

## Loneliness LCM Parameters
```{r loneliness-lgm, echo=echoChunks, message=FALSE}
```

## Loneliness Unconditional ATL Model
```{r loneliness-atl, echo=echoChunks, message=FALSE}
```

# Social Contact
## Social Contact Model Fit Indices
```{r social-contact-model-summaries, echo=echoChunks, message=FALSE}
```

## Social Contact LCM Parameters
```{r social-contact-lgm, echo=echoChunks, message=FALSE}
```

## Social Contact Unconditional ATL Model
```{r social-contact-atl, echo=echoChunks, message=FALSE}
```

# Social Strain
## Social Strain Model Fit Indices
```{r social-strain-model-summaries, echo=echoChunks, message=FALSE}
```

## Social Strain LCM Parameters
```{r social-strain-lgm, echo=echoChunks, message=FALSE}
```

## Social Strain Unconditional ATL Model
```{r social-strain-atl, echo=echoChunks, message=FALSE}
```

# Social Support
## Social Support Model Fit Indices
```{r social-support-model-summaries, echo=echoChunks, message=FALSE}
```

## Social Support LGCM Parameters
```{r social-support-lgm, echo=echoChunks, message=FALSE}
```

## Social Support LGCM Parameters
```{r social-support-atl, echo=echoChunks, message=FALSE}
```

# Depression
## Depression Model Fit Indices
```{r depression-model-summaries, echo=echoChunks, message=FALSE}
```

## Depression LGCM Parameters
```{r depression-lgm, echo=echoChunks, message=FALSE}
```

## Depression Unconditional ATL Model
```{r depression-atl, echo=echoChunks, message=FALSE}
```

# Bivariate ALT Models

## Bivariate ALT Immediate Word Recall and Social Contact
### Model Estimated

A series of models were estimated in line with the suggestion of Bollen and Curran (2004, 2006) to ensure
that the complexity of the final bivariate ALT model is warranted for each cognitive-social combination. 

Model 1: Bivariate LCM, full model
Model 2: Autoregressive, full model
Model 3: ALT, full model
Model 4: ALT, nested LCM model
Model 5: ALT, no slope variance on cognitive variable
Model 6: ALT, no slope on cognitive variable
Model 7: ALT, no slope variance on social variable
Model 8: ALT, no slope on social variable
Model 9: ALT, no time-specific uniquenesses correlations
Model 10: ALT, fixed time-specific uniquenesses correlations
Model 11: ALT, fixed autoregressions for cognitive variable
Model 12: ALT, fixed autogregressions for social variable
Model 13: ALT, fixed social-> cognitive regressions
Model 14: ALT, fixed cognitive -> social regressions

```{r, out.width = "5000px"}
knitr::include_graphics("ATL bivariate model immediate word recall social contact.pdf")
```

<img src="ATL bivariate model immediate word recall social contact.pdf" alt="some text"  width="10000" height="5200">

Significant associations only
<img src="ATL bivariate model immediate word recall social contact sig.pdf" alt="some text"  width="6200" height="5200">

## Bivariate ALT Immediate Word Recall and Loneliness
<img src="ATL bivariate model immediate word recall loneliness sig.pdf" alt="some text"  width="6200" height="5200">

## Bivariate ALT Immediate Word Recall and Depressive Symptoms
<img src="ATL bivariate model immediate word recall depression sig.pdf" alt="some text"  width="6200" height="5200">

## Bivariate ALT Immediate Word Recall and Social Support
<img src="ATL bivariate model immediate word recall social support sig.pdf" alt="some text"  width="6200" height="5200">

## Bivariate ALT Immediate Word Recall and Social Network
<img src="ATL bivariate model immediate word recall social network sig.pdf" alt="some text"  width="6200" height="5200">

## Bivariate ALT Delayed Word Recall and Loneliness
<img src="ATL bivariate model delayed word recall loneliness sig.pdf" alt="some text"  width="6200" height="5200">

## Bivariate ALT Delayed Word Recall and Social Contact
<img src="ATL bivariate model delayed word recall social contact sig.pdf" alt="some text"  width="6200" height="5200">

## Bivariate ALT Delayed Word Recall and Social Network
<img src="ATL bivariate model delayed word recall social network sig.pdf" alt="some text"  width="6200" height="5200">

## Bivariate ALT Delayed Word Recall and Social Support
<img src="ATL bivariate model delayed word recall social support sig.pdf" alt="some text"  width="6200" height="5200">

## Bivariate ALT Delayed Word Recall and Depression
<img src="ATL bivariate model delayed word recall depression.pdf" alt="some text"  width="6200" height="5200">

## Bivariate ALT Mental Status and Loneliness
<img src="ALT bivariate quadratic mental status and loneliness sig.pdf" alt="some text"  width="6200" height="5200">

## Bivariate ALT Mental Status and Social Contact
<img src="ALT bivariate quadratic mental status and social contact sig.pdf" alt="some text"  width="6200" height="5200">

## Bivariate ALT Mental Status and social network
<img src="ALT bivariate quadratic mental status and social network sig.pdf" alt="some text"  width="6200" height="5200">

## Bivariate ALT Mental Status and Social Support
<img src="ALT bivariate quadratic mental status and social support sig.pdf" alt="some text"  width="6200" height="5200">

## Bivariate ALT Mental Status and Depressive Symptoms
<img src="ALT bivariate quadratic mental status and depression sig.pdf" alt="some text"  width="6200" height="5200">