---
title: "Results"
output:
  html_document:
    theme: simplex
    toc: true
    toc_depth: 3
    keep_md: true
    toc_float: true
  word_document:
    toc: yes
date: 'Date: `r Sys.Date()`'
---
<!-- These two chunks should be added in the beginning of every .Rmd that you want to source an .R script -->
<!--  The 1st mandatory chunck  -->
<!--  Set the working directory to the repository's base directory -->
```{r, echo=F, message=F} 
#Don't combine this call with any other chunk 
# cat("Working directory: ", getwd()) # check where you are
  library(knitr)
# Rmd is in "./reports/reportA/reportA.Rmd", but now the root is "./"
  knitr::opts_knit$set(root.dir='../../') 
```


<!--  The 2nd mandatory chunck  -->
<!-- Set the report-wide options, and point to the external code file. -->
```{r set_options, echo=F}
# set options shared by all chunks
opts_chunk$set(
  results='show', 
  message = TRUE,
  comment = NA, 
  tidy = FALSE,
  fig.height = 5, 
  fig.width = 7, 
  out.width = "750px", #550px
  fig.path = 'figure_rmd/',     
  dev = "png",
  dpi = 800
  # fig.path = 'figure_pdf/',     
  # dev = "pdf"#,
  # dev.args=list(pdf = list(colormodel = 'cmyk'))
)
echoChunks <- FALSE
options(width=120 ) #So the output is 50% wider than the default.
# connect to the file with the underlying R script  
read_chunk("./sandbox/results-section/model-results.R") 
```

<!-- Load 'sourced' R files.  Suppress the output when loading packages. --> 
```{r load-packages, echo=echoChunks, message=FALSE}
```


<!-- Load the sources.  Suppress the output when loading sources. --> 
```{r load-sources, echo=echoChunks, message=FALSE}
```

# Immediate Word Recall
## Immediate Word Recall Model Fit Indices
```{r immediate-word-recall-model-summaries, echo=echoChunks, message=FALSE}
```

## Immediate Word Recall LCM Parameters
```{r immediate-word-recall-lgm, echo=echoChunks, message=FALSE}
```

## Immediate Word Recall Unconditional ATL Model
```{r immediate-word-recall-atl, echo=echoChunks, message=FALSE}
```

# Delayed Word Recall
## Delayed Word Recall Model Fit Indices
```{r delayed-word-recall-model-summaries, echo=echoChunks, message=FALSE}
```

# Delayed Word Recall LCM Parameters
```{r delayed-word-recall-lgm, echo=echoChunks, message=FALSE}
```

## Delayed Word Recall Unconditional ATL Model
```{r delayed-word-recall-atl, echo=echoChunks, message=FALSE}
```

# Mental Status
## Mental Status Model Fit Indices
```{r mental-status-model-summaries, echo=echoChunks, message=FALSE}
```

# Mental Status LCM Parameters
```{r mental-status-lgm, echo=echoChunks, message=FALSE}
```

## Mental Status Unconditional ATL Model
```{r mental-status-atl, echo=echoChunks, message=FALSE}
```

# Loneliness
## Loneliness Model Fit Indices
```{r loneliness-model-summaries, echo=echoChunks, message=FALSE}
```

# Loneliness LCM Parameters
```{r loneliness-lgm, echo=echoChunks, message=FALSE}
```

## Loneliness Unconditional ATL Model
```{r loneliness-atl, echo=echoChunks, message=FALSE}
```

# Social Contact
## Social Contact Model Fit Indices
```{r social-contact-model-summaries, echo=echoChunks, message=FALSE}
```

# Social Contact LCM Parameters
```{r social-contact-lgm, echo=echoChunks, message=FALSE}
```

## Social Contact Unconditional ATL Model
```{r social-contact-atl, echo=echoChunks, message=FALSE}
```

# Social Strain
## Social Strain Model Fit Indices
```{r social-strain-model-summaries, echo=echoChunks, message=FALSE}
```

# Social Strain LCM Parameters
```{r social-strain-lgm, echo=echoChunks, message=FALSE}
```

## Social Strain Unconditional ATL Model
```{r social-strain-atl, echo=echoChunks, message=FALSE}
```

## Social Support
## Social Support Model Fit Indices
```{r social-support-model-summaries, echo=echoChunks, message=FALSE}
```

## Social Support LGCM Parameters
```{r social-support-lgm, echo=echoChunks, message=FALSE}
```

# Social Support LGCM Parameters
```{r social-support-atl, echo=echoChunks, message=FALSE}
```

